An empirical assessment of strategies to model opponent effects in crash severity analysis

### 2020-01-16 Interactions-Crash-Severity-v1/Interactions-Crash-Severity-v1.tex
Completed work with Model 3 Ensemble

  \title{An empirical assessment of strategies to model opponent effects in crash
severity analysis}
    \author[Some University]{Author 1\corref{Corresponding Author}}
   \ead{a1@example.com} 
    \author[Some Institute of Technology]{Author 2}
   \ead{a2@example.com} 
      \address[Some University]{Department, Street, City, State, Zip}
    \address[Some Institute of Technology]{Department, Street, City, State, Zip}

@@

\caption{\label{tab:table-ape-results}\label{tab:ape-results}Predicted shares and average prediction errors (APE) by model (percentages)}
\centering
\fontsize{7}{9}\selectfont
\begin{tabular}[t]{lrrrrrrrrrr}
\toprule
\multicolumn{1}{c}{} & \multicolumn{3}{c}{No Injury} & \multicolumn{3}{c}{Injury} & \multicolumn{3}{c}{Fatality} & \multicolumn{1}{c}{} \\
\cmidrule(l{3pt}r{3pt}){2-4} \cmidrule(l{3pt}r{3pt}){5-7} \cmidrule(l{3pt}r{3pt}){8-10}
Model & Observed & Predicted & APE & Observed & Predicted & APE & Observed & Predicted & APE & WAPE\\
\rowcolor{gray!15}
\midrule
\addlinespace[0.3em]
\multicolumn{11}{l}{\textbf{In-sample (nowcasting using 2017 dataset, i.e., estimation dataset)}}\\
\hspace{1em}Model 1 & 78886 & 79029.00 & 0.18 & 84675 & 84533.74 & 0.17 & 950 & 948.26 & 0.18 & 0.17\\
\rowcolor{gray!15}
\hspace{1em}Model 2 & 78886 & 78928.98 & 0.05 & 84675 & 84641.94 & 0.04 & 950 & 940.08 & 1.04 & 0.05\\
\hspace{1em}Model 3 & 78886 & 79027.29 & 0.18 & 84675 & 84512.50 & 0.19 & 950 & 971.21 & 2.23 & 0.20\\
\rowcolor{gray!15}
\hspace{1em}Model 4 & 78886 & 78939.18 & 0.07 & 84675 & 84622.54 & 0.06 & 950 & 949.28 & 0.08 & 0.06\\
\hspace{1em}Model 1 Ensemble & 62413 & 62402.78 & 0.02 & 83564 & 83573.58 & 0.01 & 931 & 931.64 & 0.07 & 0.01\\
\rowcolor{gray!15}
\hspace{1em}Model 2 Ensemble & 62417 & 62407.00 & 0.02 & 83595 & 83604.14 & 0.01 & 931 & 931.86 & 0.09 & 0.01\\
\rowcolor{gray!15}
\hspace{1em}Model 4 Ensemble & 62405 & 62395.28 & 0.02 & 83578 & 83586.75 & 0.01 & 932 & 932.97 & 0.10 & 0.01\\
\rowcolor{gray!15}
\addlinespace[0.3em]
\multicolumn{11}{l}{\textbf{Out-of-sample (backcasting using 2016 dataset)}}\\
\hspace{1em}Model 1 & 96860 & 96364.67 & 0.51 & 101605 & 102002.59 & 0.39 & 1109 & 1206.74 & 8.81 & 0.50\\
\hspace{1em}Model 2 & 96860 & 96361.41 & 0.51 & 101605 & 102112.08 & 0.50 & 1109 & 1100.51 & 0.77 & 0.51\\
\rowcolor{gray!15}
\hspace{1em}Model 3 & 96860 & 96354.01 & 0.52 & 101605 & 102086.18 & 0.47 & 1109 & 1133.82 & 2.24 & 0.51\\
\hspace{1em}Model 4 & 96860 & 96325.85 & 0.55 & 101605 & 102136.72 & 0.52 & 1109 & 1111.43 & 0.22 & 0.54\\
\rowcolor{gray!15}
\hspace{1em}Model 1 Ensemble & 77457 & 76822.49 & 0.82 & 100013 & 100580.60 & 0.57 & 1072 & 1138.91 & 6.24 & 0.71\\
\hspace{1em}Model 2 Ensemble & 77459 & 76799.11 & 0.85 & 100049 & 100630.48 & 0.58 & 1071 & 1149.41 & 7.32 & 0.74\\
\hspace{1em}Model 4 Ensemble & 77461 & 76766.08 & 0.90 & 100029 & 100630.21 & 0.60 & 1070 & 1163.71 & 8.76 & 0.78\\
\bottomrule
\end{tabular}
\end{table}
\end{landscape}

@@

\caption{\label{tab:nowcast-outcomes-assessment}\label{tab:nowcast-outcomes-assessment}Assessment of in-sample outcomes (nowcasting using 2017 dataset, i.e., estimation dataset)}
\centering
\resizebox{\linewidth}{!}{
\fontsize{7}{9}\selectfont
\begin{tabular}[t]{lrrrrrrrrrrrrr}
\toprule
\multicolumn{1}{c}{Observed} & \multicolumn{3}{c}{Predicted Outcome} & \multicolumn{10}{c}{Verification Statistics} \\
\cmidrule(l{3pt}r{3pt}){1-1} \cmidrule(l{3pt}r{3pt}){2-4} \cmidrule(l{3pt}r{3pt}){5-14}
Outcome & No Injury & Injury & Fatality & \makecell[l]{Percent\\Correct} & \makecell[l]{Percent\\Correct\\by Class} & Bias$^1$ & \makecell[l]{Critical\\Success\\Index$^2$} & \makecell[l]{Probability of\\False\\Detection$^3$} & \makecell[l]{Probability\\of\\Detection$^4$} & \makecell[l]{False\\Alarm\\Ratio$^5$} & \makecell[l]{Heidke\\Skill\\Score$^6$} & \makecell[l]{Peirce\\Skill\\Score$^7$} & \makecell[l]{Gerrity\\Score$^8$}\\
\midrule
\addlinespace[0.3em]
\multicolumn{14}{l}{\textbf{Model 1}}\\
\hspace{1em}No Injury & 50652 & 22503 & 150 &  & 69.068 & 0.929 & 0.499 & 0.265 & 0.642 & 0.309 &  &  & \\

\hspace{1em}Injury & 28232 & 62121 & 797 &  & 68.645 & 1.076 & 0.546 & 0.364 & 0.734 & 0.318 &  &  & \\

Fatality & 2 & 51 & 3 & \multirow{-3}{*}{\raggedleft\arraybackslash 68.552} & 99.392 & 0.059 & 0.003 & 0.000 & 0.003 & 0.946 & \multirow{-3}{*}{\raggedleft\arraybackslash 0.372} & \multirow{-3}{*}{\raggedleft\arraybackslash 0.370} & \multirow{-3}{*}{\raggedleft\arraybackslash 0.190}\\
\cmidrule{1-14}
\addlinespace[0.3em]
\multicolumn{14}{l}{\textbf{Model 2}}\\
\hspace{1em}No Injury & 51531 & 17137 & 85 &  & 72.903 & 0.872 & 0.536 & 0.201 & 0.653 & 0.250 &  &  & \\

\hspace{1em}Injury & 27355 & 67514 & 864 &  & 72.415 & 1.131 & 0.598 & 0.353 & 0.797 & 0.295 &  &  & \\

Fatality & 0 & 24 & 1 & \multirow{-3}{*}{\raggedleft\arraybackslash 72.364} & 99.409 & 0.026 & 0.001 & 0.000 & 0.001 & 0.960 & \multirow{-3}{*}{\raggedleft\arraybackslash 0.447} & \multirow{-3}{*}{\raggedleft\arraybackslash 0.443} & \multirow{-3}{*}{\raggedleft\arraybackslash 0.227}\\
\cmidrule{1-14}
\addlinespace[0.3em]
\multicolumn{14}{l}{\textbf{Model 3}}\\
\hspace{1em}No Injury & 51101 & 17296 & 79 &  & 72.549 & 0.868 & 0.531 & 0.203 & 0.648 & 0.254 &  &  & \\

\hspace{1em}Injury & 27785 & 67338 & 868 &  & 72.044 & 1.134 & 0.594 & 0.359 & 0.795 & 0.298 &  &  & \\

Fatality & 0 & 41 & 3 & \multirow{-3}{*}{\raggedleft\arraybackslash 71.996} & 99.399 & 0.046 & 0.003 & 0.000 & 0.003 & 0.932 & \multirow{-3}{*}{\raggedleft\arraybackslash 0.440} & \multirow{-3}{*}{\raggedleft\arraybackslash 0.436} & \multirow{-3}{*}{\raggedleft\arraybackslash 0.224}\\
\cmidrule{1-14}
\addlinespace[0.3em]
\multicolumn{14}{l}{\textbf{Model 4}}\\
\hspace{1em}No Injury & 51575 & 17316 & 84 &  & 72.822 & 0.874 & 0.536 & 0.203 & 0.654 & 0.252 &  &  & \\

\hspace{1em}Injury & 27311 & 67336 & 863 &  & 72.334 & 1.128 & 0.597 & 0.353 & 0.795 & 0.295 &  &  & \\

Fatality & 0 & 23 & 3 & \multirow{-3}{*}{\raggedleft\arraybackslash 72.283} & 99.410 & 0.027 & 0.003 & 0.000 & 0.003 & 0.885 & \multirow{-3}{*}{\raggedleft\arraybackslash 0.446} & \multirow{-3}{*}{\raggedleft\arraybackslash 0.441} & \multirow{-3}{*}{\raggedleft\arraybackslash 0.227}\\
\cmidrule{1-14}
\addlinespace[0.3em]
\multicolumn{14}{l}{\textbf{Model 1 Ensemble}}\\
\hspace{1em}No Injury & 34664 & 16434 & 63 &  & 69.882 & 0.820 & 0.439 & 0.195 & 0.555 & 0.322 &  &  & \\

\hspace{1em}Injury & 27749 & 67120 & 829 &  & 69.354 & 1.145 & 0.599 & 0.451 & 0.803 & 0.299 &  &  & \\

Fatality & 0 & 10 & 39 & \multirow{-3}{*}{\raggedleft\arraybackslash 69.311} & 99.386 & 0.053 & 0.041 & 0.000 & 0.042 & 0.204 & \multirow{-3}{*}{\raggedleft\arraybackslash 0.363} & \multirow{-3}{*}{\raggedleft\arraybackslash 0.352} & \multirow{-3}{*}{\raggedleft\arraybackslash 0.201}\\
\cmidrule{1-14}
\addlinespace[0.3em]
\multicolumn{14}{l}{\textbf{Model 2 Ensemble}}\\
\hspace{1em}No Injury & 35443 & 16145 & 60 &  & 70.615 & 0.827 & 0.451 & 0.192 & 0.568 & 0.314 &  &  & \\

\hspace{1em}Injury & 26974 & 67437 & 829 &  & 70.083 & 1.139 & 0.605 & 0.439 & 0.807 & 0.292 &  &  & \\

Fatality & 0 & 13 & 42 & \multirow{-3}{*}{\raggedleft\arraybackslash 70.042} & 99.386 & 0.059 & 0.044 & 0.000 & 0.045 & 0.236 &  &  & \multirow{-3}{*}{\raggedleft\arraybackslash 0.211}\\

\addlinespace[0.3em]
\multicolumn{14}{l}{\textbf{Model 4 Ensemble}}\\
\hspace{1em}No Injury & 35553 & 16297 & 59 &  & 70.590 & 0.832 & 0.451 & 0.194 & 0.570 & 0.315 &  &  & \\

\hspace{1em}Injury & 26852 & 67271 & 827 &  & 70.060 & 1.136 & 0.605 & 0.437 & 0.805 & 0.292 &  &  & \\

Fatality & 0 & 10 & 46 & \multirow{-3}{*}{\raggedleft\arraybackslash 70.020} & 99.390 & 0.060 & 0.049 & 0.000 & 0.049 & 0.179 & \multirow{-6}{*}{\raggedleft\arraybackslash 0.378} & \multirow{-6}{*}{\raggedleft\arraybackslash 0.368} & \multirow{-3}{*}{\raggedleft\arraybackslash 0.213}\\
\bottomrule
\multicolumn{14}{l}{\textit{Notes: }}\\
\multicolumn{14}{l}{\textsuperscript{1} $B>1$: class is overpredicted; $B<1$: class is underpredicted; }\\
\multicolumn{14}{l}{\textsuperscript{2} $CSI = 1$: perfect score; $CSI = 0$: no skill; }\\
\multicolumn{14}{l}{\textsuperscript{3} $F = 0$: perfect score; }\\
\multicolumn{14}{l}{\textsuperscript{4} $POD = 1$: perfect score; }\\
\multicolumn{14}{l}{\textsuperscript{5} $FAR = 0$: perfect score; }\\
\multicolumn{14}{l}{\textsuperscript{6} $HSS = 1$: perfect score; $HSS = 0$: no skill; $HSS < 0$: random is better; }\\
\multicolumn{14}{l}{\textsuperscript{7} $PSS = 1$: perfect score; $PSS = 0$: no skill; }\\
\multicolumn{14}{l}{\textsuperscript{8} $GS = 1$: perfect score; $GS = 0$: no skill.}\\
\end{tabular}}
\end{table}

@@

\caption{\label{tab:backcast-outcomes-assessment}\label{tab:nowcast-outcomes-assessment}Assessment of in-sample outcomes (nowcasting using 2017 dataset, i.e., estimation dataset)}
\centering
\resizebox{\linewidth}{!}{
\fontsize{7}{9}\selectfont
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{lrrrrrrrrrrrrr}
\toprule
\multicolumn{1}{c}{Observed} & \multicolumn{3}{c}{Predicted Outcome} & \multicolumn{10}{c}{Verification Statistics} \\
\cmidrule(l{3pt}r{3pt}){1-1} \cmidrule(l{3pt}r{3pt}){2-4} \cmidrule(l{3pt}r{3pt}){5-14}
Outcome & No Injury & Injury & Fatality & \makecell[l]{Percent\\Correct} & \makecell[l]{Percent\\Correct\\by Class} & Bias$^1$ & \makecell[l]{Critical\\Success\\Index$^2$} & \makecell[l]{Probability of\\False\\Detection$^3$} & \makecell[l]{Probability\\of\\Detection$^4$} & \makecell[l]{False\\Alarm\\Ratio$^5$} & \makecell[l]{Heidke\\Skill\\Score$^6$} & \makecell[l]{Peirce\\Skill\\Score$^7$} & \makecell[l]{Gerrity\\Score$^8$}\\
\midrule
\addlinespace[0.3em]
\multicolumn{14}{l}{\textbf{Model 1}}\\
\hspace{1em}No Injury & 61684 & 27447 & 184 &  & 68.529 & 0.922 & 0.495 & 0.269 & 0.637 & 0.309 &  &  & \\

\hspace{1em}Injury & 35171 & 74073 & 915 &  & 68.123 & 1.084 & 0.538 & 0.368 & 0.729 & 0.328 &  &  & \\

Fatality & 5 & 85 & 10 & \multirow{-3}{*}{\raggedleft\arraybackslash 68.028} & 99.404 & 0.090 & 0.008 & 0.000 & 0.009 & 0.900 & \multirow{-3}{*}{\raggedleft\arraybackslash 0.363} & \multirow{-3}{*}{\raggedleft\arraybackslash 0.360} & \multirow{-3}{*}{\raggedleft\arraybackslash 0.188}\\
\cmidrule{1-14}
\addlinespace[0.3em]
\multicolumn{14}{l}{\textbf{Model 2}}\\
\hspace{1em}No Injury & 62735 & 21013 & 106 &  & 72.319 & 0.866 & 0.532 & 0.206 & 0.648 & 0.252 &  &  & \\

\hspace{1em}Injury & 34125 & 80569 & 996 &  & 71.862 & 1.139 & 0.589 & 0.358 & 0.793 & 0.304 &  &  & \\

Fatality & 0 & 23 & 7 & \multirow{-3}{*}{\raggedleft\arraybackslash 71.808} & 99.436 & 0.027 & 0.006 & 0.000 & 0.006 & 0.767 & \multirow{-3}{*}{\raggedleft\arraybackslash 0.437} & \multirow{-3}{*}{\raggedleft\arraybackslash 0.434} & \multirow{-3}{*}{\raggedleft\arraybackslash 0.224}\\
\cmidrule{1-14}
\addlinespace[0.3em]
\multicolumn{14}{l}{\textbf{Model 3}}\\
\hspace{1em}No Injury & 62248 & 21133 & 107 &  & 72.014 & 0.862 & 0.527 & 0.207 & 0.643 & 0.254 &  &  & \\

\hspace{1em}Injury & 34610 & 80433 & 996 &  & 71.550 & 1.142 & 0.586 & 0.363 & 0.792 & 0.307 &  &  & \\

>>>>

  \title{An empirical assessment of strategies to model opponent effects in crash
severity analysis}
    \author[]{Antonio Paez\corref{Corresponding Author}}
   \ead{paezha@mcmaster.ca} 
    \author[Louisiana State University]{Hany Hassan}
   \ead{hassan1@lsu.edu} 
    \author[McMaster University]{Mark Ferguson}
   \ead{fergumr@mcmaster.ca} 
    \author[McMaster University]{Saiedeh Razavi}
   \ead{razavi@mcmaster.ca} 
      \address[McMaster University]{McMaster Institute for Transportation and Logistics, 1280 Main Street
West, Hamilton, Ontario, Canada L8S 4K1}
    \address[Louisiana State University]{Department of Civil and Environmental Engineering, Baton Rouge,
Louisiana, USA 70803}

@@

\caption{\label{tab:table-ape-results}\label{tab:ape-results}Predicted shares and average prediction errors (APE) by model (percentages)}
\centering
\fontsize{7}{9}\selectfont
\begin{tabular}[t]{lrrrrrrrrrr}
\toprule
\multicolumn{1}{c}{} & \multicolumn{3}{c}{No Injury} & \multicolumn{3}{c}{Injury} & \multicolumn{3}{c}{Fatality} & \multicolumn{1}{c}{} \\
\cmidrule(l{3pt}r{3pt}){2-4} \cmidrule(l{3pt}r{3pt}){5-7} \cmidrule(l{3pt}r{3pt}){8-10}
Model & Observed & Predicted & APE & Observed & Predicted & APE & Observed & Predicted & APE & WAPE\\
\rowcolor{gray!15}
\midrule
\addlinespace[0.3em]
\multicolumn{11}{l}{\textbf{In-sample (nowcasting using 2017 dataset, i.e., estimation dataset)}}\\
\hspace{1em}Model 1 & 78886 & 79029.00 & 0.18 & 84675 & 84533.74 & 0.17 & 950 & 948.26 & 0.18 & 0.17\\
\rowcolor{gray!15}
\hspace{1em}Model 2 & 78886 & 78928.98 & 0.05 & 84675 & 84641.94 & 0.04 & 950 & 940.08 & 1.04 & 0.05\\
\hspace{1em}Model 3 & 78886 & 79027.29 & 0.18 & 84675 & 84512.50 & 0.19 & 950 & 971.21 & 2.23 & 0.20\\
\rowcolor{gray!15}
\hspace{1em}Model 4 & 78886 & 78939.18 & 0.07 & 84675 & 84622.54 & 0.06 & 950 & 949.28 & 0.08 & 0.06\\
\hspace{1em}Model 1 Ensemble & 62413 & 62402.78 & 0.02 & 83564 & 83573.58 & 0.01 & 931 & 931.64 & 0.07 & 0.01\\
\rowcolor{gray!15}
\hspace{1em}Model 2 Ensemble & 62417 & 62407.00 & 0.02 & 83595 & 83604.14 & 0.01 & 931 & 931.86 & 0.09 & 0.01\\
\rowcolor{gray!15}
\hspace{1em}Model 3 Ensemble & 62411 & 62401.23 & 0.02 & 83596 & 83604.71 & 0.01 & 933 & 934.06 & 0.11 & 0.01\\
\hspace{1em}Model 4 Ensemble & 62405 & 62395.28 & 0.02 & 83578 & 83586.75 & 0.01 & 932 & 932.97 & 0.10 & 0.01\\
\rowcolor{gray!15}
\addlinespace[0.3em]
\multicolumn{11}{l}{\textbf{Out-of-sample (backcasting using 2016 dataset)}}\\
\hspace{1em}Model 1 & 96860 & 96364.67 & 0.51 & 101605 & 102002.59 & 0.39 & 1109 & 1206.74 & 8.81 & 0.50\\
\rowcolor{gray!15}
\hspace{1em}Model 2 & 96860 & 96361.41 & 0.51 & 101605 & 102112.08 & 0.50 & 1109 & 1100.51 & 0.77 & 0.51\\
\hspace{1em}Model 3 & 96860 & 96354.01 & 0.52 & 101605 & 102086.18 & 0.47 & 1109 & 1133.82 & 2.24 & 0.51\\
\rowcolor{gray!15}
\hspace{1em}Model 4 & 96860 & 96325.85 & 0.55 & 101605 & 102136.72 & 0.52 & 1109 & 1111.43 & 0.22 & 0.54\\
\hspace{1em}Model 1 Ensemble & 77457 & 76822.49 & 0.82 & 100013 & 100580.60 & 0.57 & 1072 & 1138.91 & 6.24 & 0.71\\
\rowcolor{gray!15}
\hspace{1em}Model 2 Ensemble & 77459 & 76799.11 & 0.85 & 100049 & 100630.48 & 0.58 & 1071 & 1149.41 & 7.32 & 0.74\\
\hspace{1em}Model 3 Ensemble & 77459 & 76786.76 & 0.87 & 100050 & 100644.29 & 0.59 & 1072 & 1149.95 & 7.27 & 0.75\\
\rowcolor{gray!15}
Model 4 Ensemble & 77461 & 76766.08 & 0.90 & 100029 & 100630.21 & 0.60 & 1070 & 1163.71 & 8.76 & 0.78\\
\bottomrule
\end{tabular}
\end{table}
\end{landscape}

@@

\caption{\label{tab:nowcast-outcomes-assessment}\label{tab:nowcast-outcomes-assessment}Assessment of in-sample outcomes (nowcasting using 2017 dataset, i.e., estimation dataset)}
\centering
\resizebox{\linewidth}{!}{
\fontsize{7}{9}\selectfont
\begin{tabular}[t]{lrrrrrrrrrrrrr}
\toprule
\multicolumn{1}{c}{Observed} & \multicolumn{3}{c}{Predicted Outcome} & \multicolumn{10}{c}{Verification Statistics} \\
\cmidrule(l{3pt}r{3pt}){1-1} \cmidrule(l{3pt}r{3pt}){2-4} \cmidrule(l{3pt}r{3pt}){5-14}
Outcome & No Injury & Injury & Fatality & \makecell[l]{Percent\\Correct} & \makecell[l]{Percent\\Correct\\by Class} & Bias$^1$ & \makecell[l]{Critical\\Success\\Index$^2$} & \makecell[l]{Probability of\\False\\Detection$^3$} & \makecell[l]{Probability\\of\\Detection$^4$} & \makecell[l]{False\\Alarm\\Ratio$^5$} & \makecell[l]{Heidke\\Skill\\Score$^6$} & \makecell[l]{Peirce\\Skill\\Score$^7$} & \makecell[l]{Gerrity\\Score$^8$}\\
\midrule
\addlinespace[0.3em]
\multicolumn{14}{l}{\textbf{Model 1}}\\
\hspace{1em}No Injury & 50652 & 22503 & 150 &  & 69.0677 & 0.9293 & 0.4988 & 0.2646 & 0.6421 & 0.3090 &  &  & \\

\hspace{1em}Injury & 28232 & 62121 & 797 &  & 68.6446 & 1.0765 & 0.5463 & 0.3636 & 0.7336 & 0.3185 &  &  & \\

Fatality & 2 & 51 & 3 & \multirow{-3}{*}{\raggedleft\arraybackslash 68.5523} & 99.3921 & 0.0589 & 0.0030 & 0.0003 & 0.0032 & 0.9464 & \multirow{-3}{*}{\raggedleft\arraybackslash 0.3725} & \multirow{-3}{*}{\raggedleft\arraybackslash 0.3696} & \multirow{-3}{*}{\raggedleft\arraybackslash 0.1902}\\
\cmidrule{1-14}
\addlinespace[0.3em]
\multicolumn{14}{l}{\textbf{Model 2}}\\
\hspace{1em}No Injury & 51531 & 17137 & 85 &  & 72.9033 & 0.8715 & 0.5362 & 0.2011 & 0.6532 & 0.2505 &  &  & \\

\hspace{1em}Injury & 27355 & 67514 & 864 &  & 72.4152 & 1.1306 & 0.5980 & 0.3535 & 0.7973 & 0.2948 &  &  & \\

Fatality & 0 & 24 & 1 & \multirow{-3}{*}{\raggedleft\arraybackslash 72.3636} & 99.4086 & 0.0263 & 0.0010 & 0.0001 & 0.0011 & 0.9600 & \multirow{-3}{*}{\raggedleft\arraybackslash 0.4474} & \multirow{-3}{*}{\raggedleft\arraybackslash 0.4429} & \multirow{-3}{*}{\raggedleft\arraybackslash 0.2265}\\
\cmidrule{1-14}
\addlinespace[0.3em]
\multicolumn{14}{l}{\textbf{Model 3}}\\
\hspace{1em}No Injury & 51101 & 17296 & 79 &  & 72.5489 & 0.8680 & 0.5309 & 0.2029 & 0.6478 & 0.2537 &  &  & \\

\hspace{1em}Injury & 27785 & 67338 & 868 &  & 72.0444 & 1.1336 & 0.5942 & 0.3589 & 0.7953 & 0.2985 &  &  & \\

Fatality & 0 & 41 & 3 & \multirow{-3}{*}{\raggedleft\arraybackslash 71.9964} & 99.3994 & 0.0463 & 0.0030 & 0.0003 & 0.0032 & 0.9318 & \multirow{-3}{*}{\raggedleft\arraybackslash 0.4400} & \multirow{-3}{*}{\raggedleft\arraybackslash 0.4356} & \multirow{-3}{*}{\raggedleft\arraybackslash 0.2239}\\
\cmidrule{1-14}
\addlinespace[0.3em]
\multicolumn{14}{l}{\textbf{Model 4}}\\
\hspace{1em}No Injury & 51575 & 17318 & 84 &  & 72.8207 & 0.8744 & 0.5356 & 0.2032 & 0.6538 & 0.2523 &  &  & \\

\hspace{1em}Injury & 27311 & 67334 & 863 &  & 72.3332 & 1.1279 & 0.5967 & 0.3529 & 0.7952 & 0.2950 &  &  & \\

Fatality & 0 & 23 & 3 & \multirow{-3}{*}{\raggedleft\arraybackslash 72.2821} & 99.4104 & 0.0274 & 0.0031 & 0.0001 & 0.0032 & 0.8846 & \multirow{-3}{*}{\raggedleft\arraybackslash 0.4458} & \multirow{-3}{*}{\raggedleft\arraybackslash 0.4414} & \multirow{-3}{*}{\raggedleft\arraybackslash 0.2268}\\
\cmidrule{1-14}
\addlinespace[0.3em]
\multicolumn{14}{l}{\textbf{Model 1 Ensemble}}\\
\hspace{1em}No Injury & 34664 & 16434 & 63 &  & 69.8818 & 0.8197 & 0.4393 & 0.1952 & 0.5554 & 0.3225 &  &  & \\

\hspace{1em}Injury & 27749 & 67120 & 829 &  & 69.3536 & 1.1452 & 0.5985 & 0.4512 & 0.8032 & 0.2986 &  &  & \\

Fatality & 0 & 10 & 39 & \multirow{-3}{*}{\raggedleft\arraybackslash 69.3107} & 99.3860 & 0.0526 & 0.0414 & 0.0001 & 0.0419 & 0.2041 & \multirow{-3}{*}{\raggedleft\arraybackslash 0.3626} & \multirow{-3}{*}{\raggedleft\arraybackslash 0.3521} & \multirow{-3}{*}{\raggedleft\arraybackslash 0.2010}\\
\cmidrule{1-14}
\addlinespace[0.3em]
\multicolumn{14}{l}{\textbf{Model 2 Ensemble}}\\
\hspace{1em}No Injury & 35443 & 16145 & 60 &  & 70.6151 & 0.8275 & 0.4508 & 0.1917 & 0.5678 & 0.3138 &  &  & \\

\hspace{1em}Injury & 26974 & 67437 & 829 &  & 70.0830 & 1.1393 & 0.6054 & 0.4389 & 0.8067 & 0.2919 &  &  & \\

Fatality & 0 & 13 & 42 & \multirow{-3}{*}{\raggedleft\arraybackslash 70.0421} & 99.3862 & 0.0591 & 0.0445 & 0.0001 & 0.0451 & 0.2364 & \multirow{-3}{*}{\raggedleft\arraybackslash 0.3784} & \multirow{-3}{*}{\raggedleft\arraybackslash 0.3678} & \multirow{-3}{*}{\raggedleft\arraybackslash 0.2106}\\
\cmidrule{1-14}
\addlinespace[0.3em]
\multicolumn{14}{l}{\textbf{Model 3 Ensemble}}\\
\hspace{1em}No Injury & 35498 & 16204 & 60 &  & 70.6159 & 0.8294 & 0.4512 & 0.1924 & 0.5688 & 0.3142 &  &  & \\

\hspace{1em}Injury & 26913 & 67379 & 828 &  & 70.0844 & 1.1379 & 0.6052 & 0.4379 & 0.8060 & 0.2916 &  &  & \\

Fatality & 0 & 13 & 45 & \multirow{-3}{*}{\raggedleft\arraybackslash 70.0436} & 99.3868 & 0.0622 & 0.0476 & 0.0001 & 0.0482 & 0.2241 & \multirow{-3}{*}{\raggedleft\arraybackslash 0.3786} & \multirow{-3}{*}{\raggedleft\arraybackslash 0.3681} & \multirow{-3}{*}{\raggedleft\arraybackslash 0.2123}\\
\cmidrule{1-14}
\addlinespace[0.3em]
\multicolumn{14}{l}{\textbf{Model 4 Ensemble}}\\
\hspace{1em}No Injury & 35553 & 16297 & 59 &  & 70.5898 & 0.8318 & 0.4514 & 0.1935 & 0.5697 & 0.3151 &  &  & \\

\hspace{1em}Injury & 26852 & 67271 & 827 &  & 70.0602 & 1.1361 & 0.6046 & 0.4370 & 0.8049 & 0.2915 &  &  & \\

Fatality & 0 & 10 & 46 & \multirow{-3}{*}{\raggedleft\arraybackslash 70.0201} & 99.3901 & 0.0601 & 0.0488 & 0.0001 & 0.0494 & 0.1786 & \multirow{-3}{*}{\raggedleft\arraybackslash 0.3783} & \multirow{-3}{*}{\raggedleft\arraybackslash 0.3679} & \multirow{-3}{*}{\raggedleft\arraybackslash 0.2127}\\
\bottomrule
\multicolumn{14}{l}{\textit{Notes: }}\\
\multicolumn{14}{l}{\textsuperscript{1} $B>1$: class is overpredicted; $B<1$: class is underpredicted; }\\
\multicolumn{14}{l}{\textsuperscript{2} $CSI = 1$: perfect score; $CSI = 0$: no skill; }\\
\multicolumn{14}{l}{\textsuperscript{3} $F = 0$: perfect score; }\\
\multicolumn{14}{l}{\textsuperscript{4} $POD = 1$: perfect score; }\\
\multicolumn{14}{l}{\textsuperscript{5} $FAR = 0$: perfect score; }\\
\multicolumn{14}{l}{\textsuperscript{6} $HSS = 1$: perfect score; $HSS = 0$: no skill; $HSS < 0$: random is better; }\\
\multicolumn{14}{l}{\textsuperscript{7} $PSS = 1$: perfect score; $PSS = 0$: no skill; }\\
\multicolumn{14}{l}{\textsuperscript{8} $GS = 1$: perfect score; $GS = 0$: no skill.}\\
\end{tabular}}
\end{table}

@@

\caption{\label{tab:backcast-outcomes-assessment}\label{tab:nowcast-outcomes-assessment}Assessment of out-of-sample outcomes (backcasting using 2016 dataset)}
\centering
\resizebox{\linewidth}{!}{
\fontsize{7}{9}\selectfont
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{lrrrrrrrrrrrrr}
\toprule
\multicolumn{1}{c}{Observed} & \multicolumn{3}{c}{Predicted Outcome} & \multicolumn{10}{c}{Verification Statistics} \\
\cmidrule(l{3pt}r{3pt}){1-1} \cmidrule(l{3pt}r{3pt}){2-4} \cmidrule(l{3pt}r{3pt}){5-14}
Outcome & No Injury & Injury & Fatality & \makecell[l]{Percent\\Correct} & \makecell[l]{Percent\\Correct\\by Class} & Bias$^1$ & \makecell[l]{Critical\\Success\\Index$^2$} & \makecell[l]{Probability of\\False\\Detection$^3$} & \makecell[l]{Probability\\of\\Detection$^4$} & \makecell[l]{False\\Alarm\\Ratio$^5$} & \makecell[l]{Heidke\\Skill\\Score$^6$} & \makecell[l]{Peirce\\Skill\\Score$^7$} & \makecell[l]{Gerrity\\Score$^8$}\\
\midrule
\addlinespace[0.3em]
\multicolumn{14}{l}{\textbf{Model 1}}\\
\hspace{1em}No Injury & 61684 & 27447 & 184 &  & 68.5295 & 0.9221 & 0.4955 & 0.2690 & 0.6368 & 0.3094 &  &  & \\

\hspace{1em}Injury & 35171 & 74073 & 915 &  & 68.1231 & 1.0842 & 0.5380 & 0.3683 & 0.7290 & 0.3276 &  &  & \\

Fatality & 5 & 85 & 10 & \multirow{-3}{*}{\raggedleft\arraybackslash 68.0284} & 99.4042 & 0.0902 & 0.0083 & 0.0005 & 0.0090 & 0.9000 & \multirow{-3}{*}{\raggedleft\arraybackslash 0.3628} & \multirow{-3}{*}{\raggedleft\arraybackslash 0.3604} & \multirow{-3}{*}{\raggedleft\arraybackslash 0.1882}\\
\cmidrule{1-14}
\addlinespace[0.3em]
\multicolumn{14}{l}{\textbf{Model 2}}\\
\hspace{1em}No Injury & 62735 & 21013 & 106 &  & 72.3190 & 0.8657 & 0.5317 & 0.2056 & 0.6477 & 0.2519 &  &  & \\

\hspace{1em}Injury & 34125 & 80569 & 996 &  & 71.8616 & 1.1386 & 0.5893 & 0.3585 & 0.7930 & 0.3036 &  &  & \\

Fatality & 0 & 23 & 7 & \multirow{-3}{*}{\raggedleft\arraybackslash 71.8085} & 99.4363 & 0.0271 & 0.0062 & 0.0001 & 0.0063 & 0.7667 & \multirow{-3}{*}{\raggedleft\arraybackslash 0.4372} & \multirow{-3}{*}{\raggedleft\arraybackslash 0.4335} & \multirow{-3}{*}{\raggedleft\arraybackslash 0.2241}\\
\cmidrule{1-14}
\addlinespace[0.3em]
\multicolumn{14}{l}{\textbf{Model 3}}\\
\hspace{1em}No Injury & 62248 & 21133 & 107 &  & 72.0144 & 0.8619 & 0.5271 & 0.2068 & 0.6427 & 0.2544 &  &  & \\

\hspace{1em}Injury & 34610 & 80433 & 996 &  & 71.5504 & 1.1421 & 0.5862 & 0.3634 & 0.7916 & 0.3068 &  &  & \\
